Ensemble Stability of Biological Networks

### 2014-09-16 paper.tex
add definition of SCCs

This description can be formalized as a directed graph $G_X$ that describes the manner in which each of the variables depends upon one another given by an adjacency matrix $\adj(G_X)$ where
 \begin{displaymath}
   \adj(G_X)_{ij} = \left\{
     \begin{array}{ll}
       1, & F_i \hbox{ depends on } x_j\\
       0, & F_i \hbox{ does not depend on } x_j
     \end{array}
   \right.
\end{displaymath}
\todo{Define strongly connected components and connect to operads \cite{Vagner2014}}

>>>>

This description can be formalized as a directed graph $G_X$ that describes the manner in which each of the variables depends upon one another given by an adjacency matrix $\adj(G_X)$ where
 \begin{displaymath}
   \adj(G_X)_{ij} = \left\{
     \begin{array}{ll}
       1, & F_i \hbox{ depends on } x_j\\
       0, & F_i \hbox{ does not depend on } x_j
     \end{array}
   \right.
\end{displaymath}
A graph can be decomposed into a natural collection of \emph{modules} called strongly connected components. A strongly connected component of a graph is a maximal subset of vertices where each vertex within the subset can be reached from any other \cite{Cormen2009}. The strongly connected components of some examples of three component systems are outlined in \ref{fig:scc}.

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/scc.pdf}
\caption{{\bf Example of strongly connected components.} (A) - (D) show strongly connected components highlighted in gray for each of the four graphs representing the interdependencies relevant to four different three component systems. Note that the most hierarchical system in (A) has the highest possible number of connected components, three, whereas the system containing a single cycle and therefore posessing no hierarchy contains only one connected component. Systems (B) and (D) represent examples of hierarchical modular systems that posess both modularity and hierarchy.}
\label{fig:scc}
\end{figure}
